A fast GPU solver for near-Toeplitz tridiagonal systems

### 2015-11-03 paper-draft/paper.tex
update

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/global-vs-shared-2d.eps}
\end{center}
\label{fig:global-vs-shared-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/global-vs-shared-3d.eps}
\end{center}
\label{fig:global-vs-shared-3d}
\end{figure}

In Figures \ref{fig:global-vs-shared-2d} and \ref{fig:global-vs-shared-3d},
we report the performance of the two solvers for the case
$N_{rhs} = n$ and $N_{rhs} = n^2$.
These cases correspond to tridiagonal systems
arising in 2-D and 3-D problems respectively.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=250pt]{fig/bench-2d.eps}
\end{center}
\label{fig:k20-bench-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=250pt]{fig/bench-3d.eps}
\end{center}
\label{fig:k20-bench-3d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=250pt]{fig/phases-analysis.eps}
\end{center}
\label{fig:k20-forward-vs-backward}
\end{figure}

\input{table/global-vs-shared.tex}

\pagebreak
\section*{References}

>>>>

In this section we present a performance overview
of our Near-Toeplitz tridiagonal solver (NEATO)
against a multi-threaded Intel MKL solver and
the CUSPARSE GPU solver
(\texttt{dgtsv} and \texttt{dgtsvStridedBatch} respectively).

The CPU code is compiled with the Intel C++ compiler
and run on up to 16 cores of the
Intel Xeon Processor E5-2670 v2 (25M Cache, 2.50 GHz).
GPU code is compiled with the CUDA toolkit (version 6.5.14),
and run on the
NVIDIA Tesla K20 Accelerator.
\texttt{-O2} level optimizations are turned on for both
CPU and GPU code.

@@

\begin{figure}[!htb]
    \centering
    \begin{minipage}{0.75\textwidth}
        \centering
        \includegraphics[width=1.0\linewidth]{fig/global-vs-shared-2d.eps}
        \caption{Comparison of global memory and shared
            memory implementations of NEATO (2D problems)}
        \label{fig:global-vs-shared-2d}
    \end{minipage}
    \\
    \begin{minipage}{0.75\textwidth}
        \centering
        \includegraphics[width=1.0\linewidth]{fig/global-vs-shared-2d.eps}
        \caption{Comparison of global memory and shared memory
            implementations of NEATO (2D problems)}
        \label{fig:global-vs-shared-3d}
    \end{minipage}
\end{figure}

In Figures \ref{fig:global-vs-shared-2d} and \ref{fig:global-vs-shared-3d},
we report the performance of the two solvers for the case
$N_{rhs} = n$ and $N_{rhs} = n^2$.
These cases correspond to tridiagonal systems
arising in 2-D and 3-D problems respectively.
We note that the shared memory implementation
offers better performance in nearly all cases.
However, the relative speedup from using
shared memory diminishes with increasing problem size.
For larger problem sizes,
the reduced occupancy and increase in number of inactive threads
leads to poor shared memory performance.

\subsection{Comparison with Intel MKL and CUSPARSE solvers}

In Figures \ref{fig:bench-2d} and \ref{fig:bench-3d},
we provide the relative performance of
Intel MKL and CUSPARSE solvers and compare against
the NEATO shared memory implementation.
The Intel MKL solver can use multiple threads
to solve several systems simaltaneously.
The CUSPARSE solver uses a hybrid algorithm composed
of Cyclic Reduction and Parallel Cyclic Reduction (CR+PCR).

The relative performance for
each problem size is obtained by
normalizing the solver timings
by the timing for the fastest solver for that problem size.

Table \ref{table:bench} shows
timings for different solvers.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=300pt]{fig/bench-2d.eps}
\end{center}
\caption{Relative solver performance for 2-D problems}
\label{fig:bench-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=300pt]{fig/bench-3d.eps}
\end{center}
\caption{Relative solver performance for 3-D problems}
\label{fig:bench-3d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=300pt]{fig/phases-analysis.eps}
\end{center}
\label{fig:k20-forward-vs-backward}
\end{figure}

\begin{table}[]
\scriptsize
\centering
\caption{Performance of Intel MKL, CUSPARSE and NEATO solvers}
\label{table:bench}
\input{table/bench.tex}
\end{table}

\section{Application: compact finite difference on multiple GPUs}

\pagebreak
\pagebreak
\section*{References}
